---
title: "03_pilot_analysis"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r echo=FALSE, message=FALSE, warning=FALSE}
library(tidyverse)
library(lme4)
source("helpers.R")
library(languageR)
library(lmerTest)
library(wesanderson)
library(dplyr)
library(stringr)
cbPalette <- c("#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7")
```

Set the background to be white instead of gray.
```{r echo=FALSE, message=FALSE, warning=FALSE}
theme_set(theme_minimal())
```

```{r echo=FALSE, message=FALSE, warning=FALSE}
d <- read.csv("../../data/03_pilot/03_pilot-merged.csv")
summary(d)
#View(d)
```

Exclude participants based on first language:
```{r echo=FALSE, message=FALSE, warning=FALSE}
lang_exclude = d %>%
  select(workerid, subject_information.language) %>%
  filter(str_detect(subject_information.language,regex("english", ignore_case=TRUE),negate=TRUE)) %>%
  filter(str_detect(subject_information.language,regex("en", ignore_case=TRUE),negate=TRUE)) %>%
  filter(str_detect(subject_information.language,regex("eng", ignore_case=TRUE),negate=TRUE)) %>%
  select(workerid, subject_information.language)
d_english_1 = d[!(d$workerid %in% lang_exclude$workerid),]
#View(d_english_1)
```

Exclude participants based on confusion (yes/no):
```{r echo=FALSE, message=FALSE, warning=FALSE}
confusion_yes_no_exclude = d_english_1 %>%
  select(workerid, subject_information.asses) %>%
  filter(str_detect(subject_information.asses,regex("no", ignore_case=TRUE),negate=TRUE)) %>%
  select(workerid, subject_information.asses)
d_confusion_2 = d_english_1[(d_english_1$workerid %in% confusion_yes_no_exclude$workerid),]
#View(d_confusion_2)
```

Exclude participants based on attention check:
```{r echo=FALSE, message=FALSE, warning=FALSE}
attention_exclude = d_confusion_2 %>%
  select(workerid, attention_check.check_check) %>%
  filter(str_detect(attention_check.check_check,regex("false", ignore_case=TRUE),negate=TRUE)) %>%
  select(workerid, attention_check.check_check)
d_check_3 = d_confusion_2[(d_confusion_2$workerid %in% attention_exclude$workerid),]
#View(d_check_3)
```

Define coin column selection function:
```{r echo=FALSE, message=FALSE, warning=FALSE}
coin_cols <- function() {
  c(starts_with("coin"))
}
```

Define workerid column selection function:
```{r echo=FALSE, message=FALSE, warning=FALSE}
worker_col <- function() {
  c(starts_with("worker"))
}
```

Define mean and normalization function:
```{r echo=FALSE, message=FALSE, warning=FALSE}
norm_20 <- function(x) {
  m = mean(x)
  return(m/20)
}
```

Define bet_options:
```{r echo=FALSE, message=FALSE, warning=FALSE}

bet_options = c("coin_a"="20","coin_b"="21","coin_c"="22","coin_d"="23","coin_e"="24","coin_f"="25","coin_g"="26","coin_h"="27","coin_i"="28","coin_j"="29","coin_k"="30")
```

Get means for bets over all contexts and normalize:
```{r echo=FALSE, message=FALSE, warning=FALSE}
all_contexts_column_means =
  select(d_check_3, coin_cols()) %>%
  summarise_all(norm_20)
```

Histogram of means for all contexts:
```{r echo=FALSE, message=FALSE, warning=FALSE}

all_contexts.hist = barplot(as.numeric(all_contexts_column_means))
```

Plot bets across all contexts:
```{r echo=FALSE, message=FALSE, warning=FALSE}
#png("03_pilot_allcontexts")

pivot_all_context = pivot_longer(all_contexts_column_means, cols = 1:11, names_to = "value", values_to = "prob")

pivot_all_context$value <- str_replace_all(pivot_all_context$value, bet_options)

p <- ggplot(pivot_all_context) +
        geom_col(aes(x=value, y=prob)) +
        labs(title="03_pilot all contexts, n=78", x="Value", y="Probability")

p
ggsave(plot = p, filename = "03_pilot_allcontexts.pdf", width = 5, height = 3, units = "in")
```

Isolate no-bound contexts, get means for bets over all contexts and normalize:
```{r echo=FALSE, message=FALSE, warning=FALSE}
d_none_4 = d_check_3 %>%
  filter(bound == "none")

nobounds_means =
  select(d_none_4, coin_cols()) %>%
  summarise_all(norm_20)
```

Plot bets for no-bounds contexts:
```{r echo=FALSE, message=FALSE, warning=FALSE}
pivot_nobounds = pivot_longer(nobounds_means, cols = 1:11, names_to = "value", values_to = "prob")

pivot_nobounds$value <- str_replace_all(pivot_nobounds$value, bet_options)

p <- ggplot(pivot_nobounds) +
      geom_col(aes(x=value, y=prob)) +
      labs(title="03_pilot no-bound contexts, n=16", x="Value", y="Probability")

p
ggsave(plot = p, filename = "03_pilot_no_bounds.pdf", width = 5, height = 3, units = "in")
```

Isolate lower-bound contexts, get means for bets over all contexts and normalize:
```{r echo=FALSE, message=FALSE, warning=FALSE}
d_lower_5 = d_check_3 %>%
  filter(bound == "lower")

lowerbound_means =
  select(d_lower_5, coin_cols()) %>%
  summarise_all(norm_20)
```

Plot bets for lower-bound contexts:
```{r echo=FALSE, message=FALSE, warning=FALSE}
pivot_lowerbounds = pivot_longer(lowerbound_means, cols = 1:11, names_to = "value", values_to = "prob")

pivot_lowerbounds$value <- str_replace_all(pivot_lowerbounds$value, bet_options)

p <- ggplot(pivot_lowerbounds) +
      geom_col(aes(x=value, y=prob)) +
      labs(title="03_pilot lower-bound contexts, n=45", x="Value", y="Probability")

p
ggsave(plot = p, filename = "03_pilot_lowerbounds.pdf", width = 5, height = 3, units = "in")
```

Isolate upper-bound contexts, get means for bets over all contexts and normalize:
```{r echo=FALSE, message=FALSE, warning=FALSE}
d_upper_6 = d_check_3 %>%
  filter(bound == "upper")

upperbound_means =
  select(d_upper_6, coin_cols()) %>%
  summarise_all(norm_20)
```

Plot bets for upper-bound contexts:
```{r echo=FALSE, message=FALSE, warning=FALSE}
pivot_upperbounds = pivot_longer(upperbound_means, cols = 1:11, names_to = "value", values_to = "prob")

pivot_upperbounds$value <- str_replace_all(pivot_upperbounds$value, bet_options)

p <- ggplot(pivot_upperbounds) +
      geom_col(aes(x=value, y=prob)) +
      labs(title="03_pilot upper-bound contexts, n=17", x="Value", y="Probability")

p
ggsave(plot = p, filename = "03_pilot_upperbounds.pdf", width = 5, height = 3, units = "in")
```

Isolate lower-bound, low-stakes contexts, get means for bets over these contexts and normalize:
```{r echo=FALSE, message=FALSE, warning=FALSE}
d_lower_low_7 = d_check_3 %>%
  filter(bound == "lower") %>%
  filter(stakes == "low")

lowerbound_low_means =
  select(d_lower_low_7, coin_cols()) %>%
  summarise_all(norm_20)
```

Plot bets for lower-bound, low-stakes contexts:
```{r echo=FALSE, message=FALSE, warning=FALSE}
pivot_lowerbounds_lowstakes = pivot_longer(lowerbound_low_means, cols = 1:11, names_to = "value", values_to = "prob")

pivot_lowerbounds_lowstakes$value <- str_replace_all(pivot_lowerbounds_lowstakes$value, bet_options)

p <- ggplot(pivot_lowerbounds_lowstakes) +
      geom_col(aes(x=value, y=prob)) +
      labs(title="03_pilot lower-bound low stakes contexts, n=29", x="Value", y="Probability")

p
ggsave(plot = p, filename = "03_pilot_lowerbound_lowstakes.pdf", width = 5, height = 3, units = "in")
```

Isolate lower-bound, high-stakes contexts, get means for bets over these contexts and normalize:
```{r echo=FALSE, message=FALSE, warning=FALSE}
d_lower_high_8 = d_check_3 %>%
  filter(bound == "lower") %>%
  filter(stakes == "high")

lowerbound_high_means =
  select(d_lower_high_8, coin_cols()) %>%
  summarise_all(norm_20)
```

Plot bets for lower-bound, high-stakes contexts:
```{r echo=FALSE, message=FALSE, warning=FALSE}
pivot_lowerbounds_highstakes = pivot_longer(lowerbound_high_means, cols = 1:11, names_to = "value", values_to = "prob")

pivot_lowerbounds_highstakes$value <- str_replace_all(pivot_lowerbounds_highstakes$value, bet_options)

p <- ggplot(pivot_lowerbounds_highstakes) +
      geom_col(aes(x=value, y=prob)) +
      labs(title="03_pilot lower-bound high stakes contexts, n=16", x="Value", y="Probability")

p
ggsave(plot = p, filename = "03_pilot_lowerbound_highstakes.pdf", width = 5, height = 3, units = "in")
```

Isolate upper-bound, low-stakes contexts, get means for bets over these contexts and normalize:
```{r echo=FALSE, message=FALSE, warning=FALSE}
d_upper_low_9 = d_check_3 %>%
  filter(bound == "upper") %>%
  filter(stakes == "low")

upperbound_low_means =
  select(d_upper_low_9, coin_cols()) %>%
  summarise_all(norm_20)
```

Plot bets for upper-bound, low-stakes contexts:
```{r echo=FALSE, message=FALSE, warning=FALSE}
pivot_upperbounds_lowstakes = pivot_longer(upperbound_low_means, cols = 1:11, names_to = "value", values_to = "prob")

pivot_upperbounds_lowstakes$value <- str_replace_all(pivot_upperbounds_lowstakes$value, bet_options)

p <- ggplot(pivot_upperbounds_lowstakes) +
      geom_col(aes(x=value, y=prob)) +
      labs(title="03_pilot upper-bound low stakes contexts, n=12", x="Value", y="Probability")

p
ggsave(plot = p, filename = "03_pilot_upperbound_lowstakes.pdf", width = 5, height = 3, units = "in")
```

Isolate upper-bound, high-stakes contexts, get means for bets over these contexts and normalize:
```{r echo=FALSE, message=FALSE, warning=FALSE}
d_upper_high_10 = d_check_3 %>%
  filter(bound == "upper") %>%
  filter(stakes == "high")

upperbound_high_means =
  select(d_upper_high_10, coin_cols()) %>%
  summarise_all(norm_20)
```

Plot bets for upper-bound, high stakes contexts:
```{r echo=FALSE, message=FALSE, warning=FALSE}
pivot_upperbounds_highstakes = pivot_longer(upperbound_high_means, cols = 1:11, names_to = "value", values_to = "prob")

pivot_upperbounds_highstakes$value <- str_replace_all(pivot_upperbounds_highstakes$value, bet_options)

p <- ggplot(pivot_upperbounds_highstakes) +
      geom_col(aes(x=value, y=prob)) +
      labs(title="03_pilot upper-bound high stakes contexts, n=5", x="Value", y="Probability")

p
ggsave(plot = p, filename = "03_pilot_upperbound_highstakes.pdf", width = 5, height = 3, units = "in")
```







Isolate game night lower-bound contexts, get means for bets over these contexts and normalize:
```{r echo=FALSE, message=FALSE, warning=FALSE}
d_gamenight_lower_11 = d_check_3 %>%
  filter(bound == "lower") %>%
  filter(item == "game_night_low_lb")

ugamenight_lower_means =
  select(d_gamenight_lower_11, coin_cols()) %>%
  summarise_all(norm_20)
```

Plot bets for game night lower-bound contexts:
```{r echo=FALSE, message=FALSE, warning=FALSE}
pivot_gamenight_lower = pivot_longer(ugamenight_lower_means, cols = 1:11, names_to = "value", values_to = "prob")

pivot_gamenight_lower$value <- str_replace_all(pivot_gamenight_lower$value, bet_options)

p <- ggplot(pivot_gamenight_lower) +
      geom_col(aes(x=value, y=prob)) +
      labs(title="03_pilot game night lower-bound contexts, n=7", x="Value", y="Probability")

p
ggsave(plot = p, filename = "03_pilot_gamenight_lowerbounds.pdf", width = 5, height = 3, units = "in")
```

Isolate game night upper-bound contexts, get means for bets over these contexts and normalize:
```{r echo=FALSE, message=FALSE, warning=FALSE}
d_gamenight_upper_12 = d_check_3 %>%
  filter(bound == "upper") %>%
  filter(item == "game_night_low_ub")

ugamenight_upper_means =
  select(d_gamenight_upper_12, coin_cols()) %>%
  summarise_all(norm_20)
```

Plot bets for game night upper-bound contexts:
```{r echo=FALSE, message=FALSE, warning=FALSE}
pivot_gamenight_upper = pivot_longer(ugamenight_upper_means, cols = 1:11, names_to = "value", values_to = "prob")

pivot_gamenight_upper$value <- str_replace_all(pivot_gamenight_upper$value, bet_options)

p <- ggplot(pivot_gamenight_upper) +
      geom_col(aes(x=value, y=prob)) +
      labs(title="03_pilot game night upper-bound contexts, n=6", x="Value", y="Probability")

p
ggsave(plot = p, filename = "03_pilot_gamenight_upperbounds.pdf", width = 5, height = 3, units = "in")
```

Isolate party lower-bound contexts, get means for bets over these contexts and normalize:
```{r echo=FALSE, message=FALSE, warning=FALSE}
d_party_lower_13 = d_check_3 %>%
  filter(bound == "lower") %>%
  filter(item == "party_low_lb")

party_lower_means =
  select(d_party_lower_13, coin_cols()) %>%
  summarise_all(norm_20)
```

Plot bets for party lower-bound contexts:
```{r echo=FALSE, message=FALSE, warning=FALSE}
pivot_party_lower = pivot_longer(party_lower_means, cols = 1:11, names_to = "value", values_to = "prob")

pivot_party_lower$value <- str_replace_all(pivot_party_lower$value, bet_options)

p <- ggplot(pivot_party_lower) +
      geom_col(aes(x=value, y=prob)) +
      labs(title="03_pilot party lower-bound contexts, n=7", x="Value", y="Probability")

p
ggsave(plot = p, filename = "03_pilot_party_lowerbounds.pdf", width = 5, height = 3, units = "in")
```

Isolate party upper-bound contexts, get means for bets over these contexts and normalize:
```{r echo=FALSE, message=FALSE, warning=FALSE}
d_party_upper_14 = d_check_3 %>%
  filter(bound == "upper") %>%
  filter(item == "party_low_ub")

party_upper_means =
  select(d_party_upper_14, coin_cols()) %>%
  summarise_all(norm_20)
```

Plot bets for party upper-bound contexts:
```{r echo=FALSE, message=FALSE, warning=FALSE}
pivot_party_upper = pivot_longer(party_upper_means, cols = 1:11, names_to = "value", values_to = "prob")

pivot_party_upper$value <- str_replace_all(pivot_party_upper$value, bet_options)

p <- ggplot(pivot_party_upper) +
      geom_col(aes(x=value, y=prob)) +
      labs(title="03_pilot party upper-bound contexts, n=2", x="Value", y="Probability")

p
ggsave(plot = p, filename = "03_pilot_party_upperbounds.pdf", width = 5, height = 3, units = "in")
```

Visualize lower-bounded individual trial distributions:
```{r echo=FALSE, message=FALSE, warning=FALSE}
lower_all_trials =
  select(d_lower_5, worker_col(), coin_cols())

pivot_lower_all = pivot_longer(lower_all_trials, cols = 2:12, names_to = "value", values_to = "prob")

lowerDelim <- list("coin_a","coin_b","coin_c","coin_d","coin_e")
upperDelim <- list("coin_g","coin_h","coin_i","coin_j","coin_k")

pivot_lower_all <- pivot_lower_all %>% 
  mutate(delimit = case_when(
    value %in% lowerDelim ~ "below",
    value %in% upperDelim ~ "above",
    value == "coin_f" ~ "25"
  ))

pivot_lower_all$value <- str_replace_all(pivot_lower_all$value, bet_options)

p <- ggplot(pivot_lower_all) +
      facet_wrap(~workerid, ncol=8) +
      geom_col(aes(x=value, y=prob,fill=delimit)) + 
      theme_bw() + 
      scale_fill_brewer(palette = "RdYlBu") +
      labs(title="03_pilot lower-bounded, individual trials, n=45", x="Value", y="Probability")

p
ggsave(plot = p, filename = "03_pilot_lowerbounds_individual.pdf", width = 15, height = 9, units = "in")
```

Visualize upper-bounded individual trial distributions:
```{r echo=FALSE, message=FALSE, warning=FALSE}
upper_all_trials =
  select(d_upper_6, worker_col(), coin_cols())

pivot_upper_all = pivot_longer(upper_all_trials, cols = 2:12, names_to = "value", values_to = "prob")

lowerDelim <- list("coin_a","coin_b","coin_c","coin_d","coin_e")
upperDelim <- list("coin_g","coin_h","coin_i","coin_j","coin_k")

pivot_upper_all <- pivot_upper_all %>% 
  mutate(delimit = case_when(
    value %in% lowerDelim ~ "below",
    value %in% upperDelim ~ "above",
    value == "coin_f" ~ "25"
  ))

pivot_upper_all$value <- str_replace_all(pivot_upper_all$value, bet_options)

p <- ggplot(pivot_upper_all) +
      facet_wrap(~workerid, ncol=8) +
      geom_col(aes(x=value, y=prob,fill=delimit)) + 
      theme_bw() + 
      scale_fill_brewer(palette = "RdYlBu") +
      labs(title="03_pilot upper-bounded, individual trials, n=17", x="Value", y="Probability")

p
ggsave(plot = p, filename = "03_pilot_upperbounds_individual.pdf", width = 15, height = 5, units = "in")
```







R resources used in building these analyses:
https://www.tutorialspoint.com/how-to-find-the-average-of-a-particular-column-in-r-data-frame
https://www.datasciencemadesimple.com/get-mean-of-a-column-in-r-2/
https://dplyr.tidyverse.org/reference/summarise_all.html
https://dplyr.tidyverse.org/reference/across.html
https://dplyr.tidyverse.org/reference/dplyr_tidy_select.html
https://dplyr.tidyverse.org/reference/select.html
https://tidyselect.r-lib.org/reference/faq-selection-context.html
https://stackoverflow.com/questions/3991905/sum-rows-in-data-frame-or-matrix
https://www.youtube.com/watch?v=FUOpsBTy_as
https://tidyr.tidyverse.org/reference/gather.html
https://www.tandfonline.com/doi/pdf/10.1198/016214505000000718#:~:text=The%20Poisson%20distribution%20is%20the,as%20fitting%20the%20Poisson%20distribution.
https://en.wikipedia.org/wiki/Multinomial_distribution
https://rpubs.com/eraldagjika/715261
https://stat.ethz.ch/R-manual/R-devel/library/stats/html/Multinom.html
https://stats.oarc.ucla.edu/r/dae/multinomial-logistic-regression/
https://www.r-bloggers.com/2022/09/the-multinomial-distribution-in-r/


